\subsection{Specific Objectives}
The proposed project will contain three panels:
\begin{itemize}
    \item The farmer panel.
    \item The merchant panel
    \item The transportation panel

\end{itemize}
The farmer panel will allow farmers create an account,post their products in the project stating the quantity,
their location and the price of the produce. The merchant panel will allow merchants create an account and bid
the products. The project will also contain a transportation panel for both merchants and farmers  request transportation services.
After a successful bidding,the merchant will be able to communicate with the farmer directly and the farmer may become the supplier
of the said merchant and may decide not to post his/her produce on the dashboard but rather,deal with the merchant directly in the project.
The revenue will be generated using three business models:
\begin{itemize}
    \item \textbf{Transaction fee revenue mode} - each time a merchant wants to bid a product,
          he/she has to include additional transaction costs depending on the price of the product. Once a transaction is complete
          ,10\% of the returns to the farmer will be paid to the business  as service fees.
          This way the business(auction project) will get money from both parties. This would maximize the profit.
    \item \textbf{Affiliate revenue model } - Merchants who have their own websites can pay affiliate costs to the auction project so as to link and advertise their products.
          They shall pay the affilliate costs depending on the number of customers who are redirected to their site.
    \item \textbf{Sales revenue model} - as stated above,the business  will offer transportation services using the transportation panel at affortable rates. This way both merchants and farmers
          can easily transport their produce.
\end{itemize}